Measuring Software Ticket Quality using Statistical Analysis

### 2017-12-18 proposal/mprop.tex
Finish fixing up proposal

We would like to begin the research by conducting a statistical analysis 
over popular open source projects such as Mozilla or Apache and extract 
tickets most probably via REST APIs, however the list of projects
will be finalized once some tests will be run, and that is because
maybe some projects will have more valuable tickets for us to analyze and
we also decided that we want to analyze multiple issue tracking systems 
(e.g. Apache uses Jira \citep{jira} while Mozilla uses Bugzilla 
\citep{bugzilla}).

@@

Implementation wise, we would like to develop the application that will
perform both scraping, extraction and inspection in either Go or Java
as I am the most proficient with these two programming languages.

In order to detect what features make for a high quality ticket, we need 
to compare two \emph{similar} tickets and then analyze their components
for differences. Thus, one of the biggest issues we will be facing is how 
can we say that two tickets are similar. We have two initial approaches
that we want to test to see which one is more efficient:
  \begin{itemize}
    \item look solely at the issue tracking system and use story points
      to detect similar tickets; one limitation of this approach is that
      either the triager is not experienced and might assign wrong story
      point values or the initial story point values are not properly
      assigned and they will be corrected during the ticket's lifecycle;
    \item look at the version control system and compare changesets for
      similar work effort; however, this approach has one limitation - 
      solely looking at source code changes might not encapsulate the
      whole effort needed to solve the task (e.g. the developers on the
      team might spend extra hours only on designing the fix).
  \end{itemize}
However, this list is not final, so if we find some other method 
while running the experiment, we shall switch to that.

Finally, having similar tickets grouped together, we can then test 
the variances in component features they possess and see which features
affected the time-to-close the most.

@@

The independent variables we would like to test are:
  \begin{itemize}
    \item presence and number of stack traces in a ticket;
    \item steps to reproduce (as described above - images or text);
    \item presence of screenshots in tickets;
    \item text components (e.g. summary, description) being either 
      succinct or detailed;
    \item grammar-free textual description;
    \item overall sentiment drawn from comments (e.g. angry or calm);
    \item complex or light discussion in comments.
  \end{itemize}

In terms of dependant variables, we only have one - the time it takes
between when the ticket was created and marked as OPEN until when it
is finished and marked as CLOSED or RESOLVED.

@@

The work on the actual project in the second semester will start off 
with deciding and analyzing which repositories to use for ticket data.
We have several popular open source options, such as Apache, Mozilla or
Eclipse, so settling on a couple of options will be the first step in our
research. We believe that this step will be finished \emph{by the end of
January}.

@@

Then, concomitantly with the previous work package, we will decide on
what method to use to detect similar tickets. This step will be performed
during the creation of the tool because we can only test efficiency once
we have some tickets to validate our ideas. Thus, the proposed deadline
for this work package is \emph{the end of February} as well.

Following we will run the the tool on the tickets we have collected. This
is expected to be quite trivial once all the other work packages are 
completed as we will simply need to run the application. The expected
deadline is \emph{by 4\textsuperscript{th} of March}.

Then, the actual write-up of the paper will be structured as follows:
  \begin{itemize}
    \item write abstract, introduction, related work - this is expected
      to be completed \emph{by mid March};
    \item write methodology and how we conducted the experiment (collecting
      data, running analysis) - expected to be finished \emph{by the 
      beginning of April};
    \item write results, contributions and conclusion for the paper - 
      we expect to complete it \emph{by 18\textsuperscript{th} of April}.
  \end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{plainnat}
\bibliography{mprop}
\end{document}

>>>>

We would like to begin the research by conducting a statistical analysis 
over popular open source projects such as Mozilla or Apache and extract 
tickets most probably via REST APIs, however the list of projects
will be finalized once some tests will be run, and that is because
maybe some projects will have more valuable tickets for us to analyze and
we want to analyze multiple issue tracking systems 
(e.g. Apache uses Jira \citep{jira} while Mozilla uses Bugzilla 
\citep{bugzilla}).

@@

Implementation wise, we would like to develop the application that will
perform both scraping, extraction and inspection in either Go or Java.

In order to detect what features make for a high quality ticket, we need 
to compare two \emph{similar} tickets and then analyze their components
for differences. Thus, one of the biggest issues we will be facing is 
comparing and contrasting tickets. We have two initial approaches
that we want to test to see which one is more efficient:
  \begin{itemize}
    \item look solely at the issue tracking system and use story points
      to detect similar tickets; one limitation of this approach is that
      either the triager is not experienced and might assign wrong story
      point values or the initial story point values are not properly
      assigned and they will be corrected during the ticket's lifecycle;
    \item look at the version control system and compare changesets for
      similar work effort; however, this approach has one limitation - 
      solely looking at source code changes might not encapsulate the
      whole effort needed to solve the task (e.g. the developers on the
      team might spend extra hours only on designing the fix).
  \end{itemize}
However, this list is not final, so if we find some other method 
while running the experiment, we shall switch to that.

Finally, grouping similar tickets together allows testing 
the variances in component features they possess and see which features
affected the time-to-close the most.

@@

The independent variables proposed for testing are:
  \begin{itemize}
    \item presence and number of stack traces in a ticket;
    \item steps to reproduce (as described above - images or text);
    \item presence of screenshots in tickets;
    \item text components (e.g. summary, description) being either 
      succinct or detailed;
    \item grammar-free textual description;
    \item overall sentiment drawn from comments (e.g. angry or calm);
    \item complex or light discussion in comments.
  \end{itemize}

In terms of dependent variables, there is only one - the time it takes
between when the ticket was created and marked as OPEN until when it
is finished and marked as CLOSED or RESOLVED.

@@

The work on the actual project in the second semester will start off 
with deciding and analyzing which repositories to use for ticket data.
There are several popular open source options, such as Apache, Mozilla or
Eclipse, so settling on a couple of options will be the first step in our
research. We believe that this step will be finished \emph{by the end of
January}.

@@

Then, concomitantly with the previous work package, the method used to 
detect similar tickets will be decided on. This step will be performed
during the creation of the tool because efficiency can only be evaluated
once ideas have been validated via execution of several mock tickets. 
Thus, the proposed deadline for this work package is \emph{the end of February} as well.

Following, tickets collected will be run in the tool created as per the previous steps. 
The expected deadline is \emph{by 4\textsuperscript{th} of March}.

Then, the actual write-up of the paper will be structured as follows:
  \begin{itemize}
    \item write abstract, introduction, related work - this is expected
      to be completed \emph{by mid March};
    \item write methodology (collecting
      data, running analysis) - expected to be finished \emph{by the 
      beginning of April};
    \item write results, contributions and conclusion for the paper - 
      we expect to complete it \emph{by 18\textsuperscript{th} of April}.
  \end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{plainnat}
\bibliography{mprop}
\end{document}
